Exp 13 write-up

### 2023-08-04 writing/DGfS2023-abstract/abstract.tex
updated glossa psycholx analysis and paper

\citealt{mandelkern-etal2020} challenged this conclusion, arguing that gradient projection is an artifact of the inference task used, writing that ``inference tasks to some degree invite subjects to make the inference in question'' (p.498) and that ``we should think twice before embracing a notion of presupposition projection that is gradient based on results from inference tasks alone'' (p.497). They suggested that naturalness ratings of utterances with attitude predicates in explicit ignorance contexts (EICs), as in (\ref{second}), are more suitable to distinguishing the semantic presuppositions of factive predicates (hypothesized to be unnatural in EICs) from inferences that arise with nonfactive predicates ``for any of a variety of pragmatic reasons short of entailment or presupposition'' (p.497).

@@

\noindent
\underline{Materials.} Participants read two-sentence discourses consisting of an interrogative followed by a declarative, like (\ref{second}). In the target stimuli, the interrogatives combined the 20 factive and nonfactive predicates with the 20 complement clauses of \citealt{degen-tonhauser-openmind,degen-tonhauser-language}. The preceding declaratives implemented a three-level context condition: In the `explicit ignorance' context (\ref{second}), the declarative sentence conveyed the speaker's ignorance about the CC: If the CC is presupposed, global accommodation (taken to be default in \citealt{heim83,vds92}) is not possible and the discourse is expected to be unnatural; if the CC is not presupposed, the discourse is expected to be natural. In the other two context levels, the declarative denoted a fact relative to which the CC had a `low prior probability' (\ref{sample}a) or a `high prior probability' (\ref{sample}b); these contexts were normed in \citealt{degen-tonhauser-openmind}. Presupposition analyses (e.g., \citealt{heim83,vds92}) invariably predict global accommodation for presupposed CCs, that is, high naturalness ratings.

>>>>

\citealt{mandelkern-etal2020} challenged this conclusion, arguing that gradient projection is an artefact of the inference task used, writing that ``inference tasks to some degree invite subjects to make the inference in question'' (p.498) and that ``we should think twice before embracing a notion of presupposition projection that is gradient based on results from inference tasks alone'' (p.497). They suggested that naturalness ratings of utterances with attitude predicates in explicit ignorance contexts (EICs), as in (\ref{second}), are more suitable to distinguish the semantic presuppositions of factive predicates (hypothesized to be unnatural in EICs) from inferences that arise with nonfactive predicates ``for any of a variety of pragmatic reasons short of entailment or presupposition'' (p.497).

@@

\noindent
\underline{Materials.} Participants read two-sentence discourses consisting of a declarative followed by an interrogative, like (\ref{second}). In the target stimuli, the interrogatives combined the 20 factive and nonfactive predicates with the 20 complement clauses of \citealt{degen-tonhauser-openmind,degen-tonhauser-language}. The preceding declaratives implemented a three-level context condition: In the `explicit ignorance' context (\ref{second}), the declarative sentence conveyed the speaker's ignorance about the CC: If the CC is presupposed, global accommodation (taken to be default in \citealt{heim83,vds92}) is not possible and the discourse is expected to be unnatural; if the CC is not presupposed, the discourse is expected to be natural. In the other two context levels, the declarative denoted a fact relative to which the CC had a `low prior probability' (\ref{sample}a) or a `high prior probability' (\ref{sample}b); these contexts were normed in \citealt{degen-tonhauser-openmind}. Presupposition analyses (e.g., \citealt{heim83,vds92}) invariably predict global accommodation for presupposed CCs, that is, high naturalness ratings.
